---
title: "Trump False Claims Project"
# resource_files:
# - .httr-oauth
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    # theme: yeti
---

```{r setup, include=FALSE}

library(flexdashboard)
library(tidyverse)
library(lubridate)
library(janitor)
library(glue)
library(plotly)
library(DT)
library(googlesheets)
library(kableExtra)
library(leaflet)
# library(ggmap)
library(RColorBrewer)
library(htmlwidgets)
library(htmltools)
library(tigris)
options(tigris_class = "sf")
library(readxl)


raw_data <- read_excel("TRUMP FACT-CHECKS.xlsx", 
                                sheet = "ak", col_types = c("date", "text", 
                                                            "text", "text", "text", "text", "text", 
                                                            "text", "text", "text", "numeric", 
                                                            "text"))


glimpse(raw_data)

#clean column names
fcheck <- raw_data %>% 
  clean_names() 

names(fcheck)

#set formatting of certain columns and break out dates into own columns
fcheck <- fcheck %>% 
  mutate(
    kind_of_forum = str_trim(str_to_upper(kind_of_forum)),
    location = str_trim(str_to_upper(location)),
    category_tag1 = str_trim(str_to_upper(category_tag1)),
    category_tag2 = str_trim(str_to_upper(category_tag2)),
    category_tag3 = str_trim(str_to_upper(category_tag3)),
    category_tag4 = str_trim(str_to_upper(category_tag4)),
    year = year(date),
    month = month(date),
    day = day(date),
    day_of_week = weekdays(date, abbreviate = T),
    isoweek = isoweek(date) #isoweek starts on MONDAYS
  )

#convert certain columns to factors for DT table filter capability
fcheck <- fcheck %>% 
  mutate(
    kind_of_forum = as.factor(kind_of_forum),
    location = as.factor(location)
  )

# remove NAs from category columns 
fcheck$category_tag1 <- fcheck$category_tag1 %>% replace_na("")
fcheck$category_tag2 <- fcheck$category_tag2 %>% replace_na("")
fcheck$category_tag3 <- fcheck$category_tag3 %>% replace_na("")
fcheck$category_tag4 <- fcheck$category_tag4 %>% replace_na("")

#create combined column with all category tags together in one
fcheck$category_combined <- paste0(fcheck$category_tag1, " ", fcheck$category_tag2, " ", fcheck$category_tag3, " ", fcheck$category_tag4)

# remove NAs from link column 
fcheck$source_article <- fcheck$source_article %>% replace_na("")

#convert link to html hyperlink format
fcheck$source_article <- paste0("<a href='", fcheck$source_article, "' target='_blank'>", fcheck$source_article, "</a>")

#create table of JUST THE PREVIOUS WEEK's checks
fcheck_PREVWEEK <- fcheck %>%
  filter(date <= today("EST"),
         date >= today("EST")-7)



# COUNTS #### ----------------------------------

#total count
count_total <- fcheck %>% 
  nrow()

#total count - previous week only
count_prevweek_total <- fcheck_PREVWEEK %>% 
  nrow()


#kind of forum count
count_forum_kind <- fcheck %>% 
  count(kind_of_forum) 

#kind of forum count - previous week only
count_prevweek_forum_kind <- fcheck_PREVWEEK %>% 
  count(kind_of_forum) 


#top kind of forum 
top_forum_kind <- fcheck %>% 
  count(kind_of_forum) %>% 
  arrange(desc(n)) %>% 
  head(1) %>% 
  select(kind_of_forum) %>% 
  pull() %>% 
  str_to_title()

#top kind of forum - previous week only
top_prevweek_forum_kind <- fcheck_PREVWEEK %>% 
  count(kind_of_forum) %>% 
  arrange(desc(n)) %>% 
  head(1) %>% 
  select(kind_of_forum) %>% 
  pull() %>% 
  str_to_title()


#top forum 
top_forum <- fcheck %>% 
  count(forum) %>% 
  arrange(desc(n)) %>% 
  head(1) %>% 
  select(forum) %>% 
  pull() %>% 
  str_to_title()

#top forum - previous week only
top_prevweek_forum <- fcheck_PREVWEEK %>% 
  count(forum) %>% 
  arrange(desc(n)) %>% 
  head(1) %>% 
  select(forum) %>% 
  pull() %>% 
  str_to_title()



### count up subject categories stretching across four data columns #### --------------------
tag1 <- fcheck %>% 
  select(tag = category_tag1)

tag2 <- fcheck %>% 
  select(tag = category_tag2)

tag3 <- fcheck %>% 
  select(tag = category_tag3)

tag4 <- fcheck %>% 
  select(tag = category_tag4)

#combine into one
tag_combined <- bind_rows(tag1, tag2, tag3, tag4)

#filter out NAs
tag_combined <- tag_combined %>% 
  filter(!is.na(tag))

category_tag_count <- tag_combined %>% 
  count(tag) %>% 
  arrange(desc(n))


### Now the same for PREV WEEK ONLY
tag1b <- fcheck_PREVWEEK %>% 
  select(tag = category_tag1)

tag2b <- fcheck_PREVWEEK %>% 
  select(tag = category_tag2)

tag3b <- fcheck_PREVWEEK %>% 
  select(tag = category_tag3)

tag4b <- fcheck_PREVWEEK %>% 
  select(tag = category_tag4)

#combine into one
tag_combined <- bind_rows(tag1b, tag2b, tag3b, tag4b)

#filter out NAs
tag_combined_PREVWEEK <- tag_combined %>% 
  filter(!is.na(tag))

category_tag_PREVWEEK_count <- tag_combined_PREVWEEK %>% 
  count(tag) %>% 
  arrange(desc(n))


#subject count - all
subject_count <- category_tag_count %>% 
  nrow()

#subject count - previous week only
subject_count_PREVWEEK <- category_tag_PREVWEEK_count %>% 
  nrow()

 



# set time object set to eastern time
d <- Sys.Date()
# d <- .POSIXct(d, "EST")
  
t <- Sys.time()
t <- .POSIXct(t, "EST")

```


Searchable Database 
===================================== 
Trump false claim fact checks through `r format(d, format="%b %d")`. To filter the list, click on the boxes above the columns. To sort, click on the arrows by the column names. To search globally by keywords, use the search box on the right. 
(Last updated on `r format(t, format="%B %d %I:%M %p %Z")`)


Row 
-----------------------------------------------------------------------

### {data-width=800}

```{r searchable_table}

#searchable table

fcheck_table <- fcheck %>% 
  select(date,
         kind_of_forum,
         forum,
         location,
         claim,
         fact_check,
         category_combined,
         source_article
) %>% 
  arrange(desc(date))

datatable(fcheck_table, 
          rownames = FALSE, 
          filter = "top",
          escape = FALSE,
          options = list(searchHighlight = TRUE)) %>% 
  formatDate('date', 'toDateString') %>% 
  formatStyle('claim', fontStyle = 'italic')


```



Summary Counts (Previous Week) 
===================================== 
Aggregate counts of all Trump false claims made over the **previous seven days**. 


Row {data-height=200}
-----------------------------------------------------------------------

### Number of false claims this week

```{r }

tot <- count_prevweek_total

valueBox(tot, icon = "fa-pencil", color = "blue")


```

### Number of forum types this week

```{r}

num_forums <- count_prevweek_forum_kind %>% 
  nrow()

valueBox(num_forums, icon = "fa-users", color = "green")


```

### Number of subjects this week 

```{r}

valueBox(subject_count_PREVWEEK, icon = "fa-book", color = "darkred")



```



Row {data-height=800}
-----------------------------------------------------------------------


### Top daily totals

```{r}

bydate <- fcheck_PREVWEEK %>%
  count(date) %>% 
  head() %>% 
  ungroup() 


d <- ggplot(data = bydate, aes(x = reorder(date, -n), y = n)) +
  geom_col(
    # color = "#848484",
    fill = "lightblue") +
  # coord_flip() +
  theme_minimal()

d2 <- d + labs(x ="", y = "") +
  theme(plot.title = element_text(hjust = 0.5)) +
  # scale_fill_manual(values=cbPalette) +
  theme(legend.title=element_blank()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

dd <- ggplotly(d2)

dd_nomenu <- dd %>% config(displayModeBar = FALSE)
dd_nomenu

# ggplot(corr.m, aes(x = reorder(miRNA, -value), y = value, fill = variable)) +
#   geom_bar(stat = "identity")

```


### Top forum types

```{r}

byforumtype <- fcheck_PREVWEEK %>%
  count(kind_of_forum) %>%
  arrange(desc(n)) %>%
  head() %>%
  ungroup()


e <- ggplot(data = byforumtype, aes(x = reorder(kind_of_forum, -n), y = n)) +
  geom_col(
    # color = "#848484",
    fill = "#A8E9A8") +
  # coord_flip() +
  theme_minimal()

e2 <- e + labs(x ="", y = "") +
  theme(plot.title = element_text(hjust = 0.5)) +
  # scale_fill_manual(values=cbPalette) +
  theme(legend.title=element_blank()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ee <- ggplotly(e2)

ee_nomenu <- ee %>% config(displayModeBar = FALSE)
ee_nomenu


```


### Top subjects

```{r}

bysubject <- category_tag_PREVWEEK_count %>% 
  head()


e <- ggplot(data = bysubject, aes(x = reorder(tag, -n), y = n)) +
  geom_col(
    # color = "#848484",
    fill = "#f4a8a7") +
  # coord_flip() +
  theme_minimal()

e2 <- e + labs(x ="", y = "") +
  theme(plot.title = element_text(hjust = 0.5)) +
  # scale_fill_manual(values=cbPalette) +
  theme(legend.title=element_blank()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ee <- ggplotly(e2)

ee_nomenu <- ee %>% config(displayModeBar = FALSE)
ee_nomenu


```





Summary Counts (All) 
===================================== 
Aggregate counts of *all* Trump false claims compiled by CNN 


Row {data-height=200}
-----------------------------------------------------------------------

### Number of all false claims 

```{r count_total_box}

tot <- count_total

valueBox(tot, icon = "fa-pencil", color = "blue")


```

### Number of all forum types

```{r}

num_forums <- count_forum_kind %>% 
  nrow()

valueBox(num_forums, icon = "fa-users", color = "green")


```

### Number of all subjects 

```{r}

valueBox(subject_count, icon = "fa-book", color = "darkred")



```



Row {data-height=800}
-----------------------------------------------------------------------


### Top daily totals

```{r}

bydate <- fcheck %>%
  count(date) %>% 
  head() %>% 
  ungroup() 


d <- ggplot(data = bydate, aes(x = reorder(date, -n), y = n)) +
  geom_col(
    # color = "#848484",
    fill = "lightblue") +
  # coord_flip() +
  theme_minimal()

d2 <- d + labs(x ="", y = "") +
  theme(plot.title = element_text(hjust = 0.5)) +
  # scale_fill_manual(values=cbPalette) +
  theme(legend.title=element_blank()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

dd <- ggplotly(d2)

dd_nomenu <- dd %>% config(displayModeBar = FALSE)
dd_nomenu

# ggplot(corr.m, aes(x = reorder(miRNA, -value), y = value, fill = variable)) +
#   geom_bar(stat = "identity")

```


### Top forum types

```{r}

byforumtype <- fcheck %>%
  count(kind_of_forum) %>%
  arrange(desc(n)) %>%
  head() %>%
  ungroup()


e <- ggplot(data = byforumtype, aes(x = reorder(kind_of_forum, -n), y = n)) +
  geom_col(
    # color = "#848484",
    fill = "#A8E9A8") +
  # coord_flip() +
  theme_minimal()

e2 <- e + labs(x ="", y = "") +
  theme(plot.title = element_text(hjust = 0.5)) +
  # scale_fill_manual(values=cbPalette) +
  theme(legend.title=element_blank()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ee <- ggplotly(e2)

ee_nomenu <- ee %>% config(displayModeBar = FALSE)
ee_nomenu


```


### Top subjects

```{r}

bysubject <- category_tag_count %>% 
  head()


e <- ggplot(data = bysubject, aes(x = reorder(tag, -n), y = n)) +
  geom_col(
    # color = "#848484",
    fill = "#f4a8a7") +
  # coord_flip() +
  theme_minimal()

e2 <- e + labs(x ="", y = "") +
  theme(plot.title = element_text(hjust = 0.5)) +
  # scale_fill_manual(values=cbPalette) +
  theme(legend.title=element_blank()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ee <- ggplotly(e2)

ee_nomenu <- ee %>% config(displayModeBar = FALSE)
ee_nomenu


```





Time-based Rankings
===================================== 



Row 
-----------------------------------------------------------------------

### Top days this *past week*

```{r}

fcheck_PREVWEEK %>% 
  count(date) %>% 
  arrange(desc(n)) %>% 
  head(5) %>% 
  mutate(rank = min_rank(desc(n))) %>% 
    kable() %>%
    kable_styling(bootstrap_options = c("striped"))


```


### Top individual days (all)

```{r}

fcheck %>% 
  count(date) %>% 
  arrange(desc(n)) %>% 
  head(5) %>% 
  mutate(rank = min_rank(desc(n))) %>% 
    kable() %>%
    kable_styling(bootstrap_options = c("striped"))


```


### Top weeks 

```{r}

fcheck %>% 
  count(year, isoweek) %>% 
  arrange(desc(n)) %>% 
  head(5) %>% 
  mutate(rank = min_rank(desc(n))) %>% 
  rename(week = isoweek) %>% 
    kable() %>%
    kable_styling(bootstrap_options = c("striped"))


```


### Top months 

```{r}

fcheck %>% 
  count(year, month) %>% 
  arrange(desc(n)) %>% 
  head(5) %>% 
  mutate(rank = min_rank(desc(n))) %>% 
    kable() %>%
    kable_styling(bootstrap_options = c("striped"))


```


Row {data-height=200}
-----------------------------------------------------------------------


### Average claims this *past week*

```{r}

avg_per_day_prevweek <- fcheck_PREVWEEK %>% 
  count(date) %>% 
  summarise(mean(n)) %>% 
  pull() %>% 
  round_half_up(digits = 1)

valueBox(avg_per_day_prevweek, color = "#9c9293")

```


### Average claims per day

```{r}

avg_per_day <- fcheck %>% 
  count(date) %>% 
  summarise(mean(n)) %>% 
  pull() %>% 
  round_half_up(digits = 1)

valueBox(avg_per_day, color = "#9c9293")

```



### Average claims per week

```{r}

avg_per_week <- fcheck %>% 
  count(isoweek) %>% 
  summarise(mean(n)) %>% 
  pull()%>% 
  round_half_up(digits = 1)

valueBox(avg_per_week, color = "#9c9293")

```


### Average claims per month

```{r}

avg_per_month <- fcheck %>% 
  count(month) %>% 
  summarise(mean(n)) %>% 
  pull() %>% 
  round_half_up(digits = 1)

valueBox(avg_per_month, color = "#9c9293")

```


Row 
-----------------------------------------------------------------------

### Timeline of daily false claims

```{r}

bydate <- fcheck %>%
  count(date) 


p <- plot_ly(bydate, x = ~date, y = ~n, name = 'claimsperday', type = 'scatter',
             mode = 'lines+markers', connectgaps = TRUE)

p %>% config(displayModeBar = FALSE)





```

### TBD
