---
title: "Trump False Claims Project"
resource_files:
- .httr-oauth
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    # theme: yeti

---

```{r setup, include=FALSE}

library(flexdashboard)
library(tidyverse)
library(lubridate)
library(janitor)
library(glue)
library(plotly)
library(DT)
library(googlesheets)
library(kableExtra)
library(leaflet)
# library(ggmap)
library(RColorBrewer)
library(htmlwidgets)
library(htmltools)
library(tigris)
options(tigris_class = "sf")
library(readxl)
library(writexl)


# to authenticate the first time:
# gs_ls()

# import data from Google Sheet 
mykey <- Sys.getenv("TRUMPCLAIMS_KEY")
trumpsheet <- gs_key(mykey)

#read in data from the trump false claims tab
falseclaims <- trumpsheet %>% 
  gs_read(ws = "falseclaims") 

glimpse(falseclaims)

#clean column names
fcheck <- falseclaims %>%
  clean_names()

names(fcheck)

# filter out missing dates 
fcheck <- fcheck %>% 
  filter(!is.na(date))

#set date to date format
fcheck$date <- mdy(fcheck$date) 

#set formatting of certain columns and break out dates into own columns
fcheck <- fcheck %>%
  mutate(
    kind_of_forum = str_trim(str_to_upper(kind_of_forum)),
    location = str_trim(str_to_upper(location)),
    state = str_trim(str_to_upper(state)),
    code_name = str_trim(str_to_upper(code_name)),
    category_tags_combined = str_trim(str_to_upper(category_tags_combined)),
    year = year(date),
    month = month(date),
    day = day(date),
    day_of_week = weekdays(date, abbreviate = T),
    isoweek = isoweek(date) #isoweek starts on MONDAYS
  )

# fcheck <- readRDS("saved_versions/fcheck_saved.rds")

#convert certain columns to factors for DT table filter capability
fcheck <- fcheck %>% 
  mutate(
    kind_of_forum = as.factor(kind_of_forum),
    location = as.factor(location),
    state = as.factor(state)
  )

# remove NAs from category columns 
# fcheck$code_name <- fcheck$code_name %>% replace_na("")

#clean up extra trailing semicolons at end of combined tag column
# fcheck$category_tags_combined <- str_trim(gsub("[; ]*$", "", fcheck$category_tags_combined))

# remove NAs from link column 
fcheck$source_article <- fcheck$source_article %>% replace_na("")
fcheck$source_article_2 <- fcheck$source_article_2 %>% replace_na("")

#convert link to html hyperlink format
fcheck$source_article <- paste0("<a href='", fcheck$source_article, "' target='_blank'>", fcheck$source_article, "</a>")

fcheck$source_article_2 <- paste0("<a href='", fcheck$source_article_2, "' target='_blank'>", fcheck$source_article_2, "</a>")

#clean up empty hyperlinks
fcheck$source_article <- str_remove(fcheck$source_article, "<a href='' target='_blank'></a>")

fcheck$source_article_2 <- str_remove(fcheck$source_article_2, "<a href='' target='_blank'></a>")


#create table of JUST THE MOST RECENT MON-SUN WEEK's checks #### ------------------

dates <- today()

weekdays(dates)

wdays <- setNames(0:6, c("Monday", "Tuesday", "Wednesday",
                         "Thursday", "Friday", "Saturday", "Sunday"))

weekdays(dates - wdays[weekdays(dates)])

#find previous SUN date
most_recent_sunday <- dates - match(weekdays(dates), c("Monday", "Tuesday", "Wednesday", 
                                 "Thursday", "Friday", "Saturday", "Sunday"))

#calculate Monday before that Sunday
monday_before_recent_sunday <- most_recent_sunday - 6

#now let's try to use this to filter our dates from the table
fcheck_PREVWEEK <- fcheck %>%
  filter(date <= most_recent_sunday,
         date >= monday_before_recent_sunday) 

#formatted dates for text output string
monday_formatted <- format(monday_before_recent_sunday, "%a %b %d")
sunday_formatted <- format(most_recent_sunday, "%a %b %d")

week_range_string <- glue("week of {monday_formatted} to {sunday_formatted}")




# COUNTS #### ---------------------------------------------------------------------

#total count
count_total <- fcheck %>% 
  nrow()

#total count - previous week only
count_prevweek_total <- fcheck_PREVWEEK %>% 
  nrow()


#kind of forum count
count_forum_kind <- fcheck %>% 
  count(kind_of_forum) 

#kind of forum - previous week only
count_prevweek_forum <- fcheck_PREVWEEK %>% 
  count(forum) 


#top kind of forum 
top_forum_kind <- fcheck %>% 
  count(kind_of_forum) %>% 
  arrange(desc(n)) %>% 
  head(1) %>% 
  select(kind_of_forum) %>% 
  pull() %>% 
  str_to_title()

#top kind of forum - previous week only
top_prevweek_forum_kind <- fcheck_PREVWEEK %>% 
  count(kind_of_forum) %>% 
  arrange(desc(n)) %>% 
  head(1) %>% 
  select(kind_of_forum) %>% 
  pull() %>% 
  str_to_title()


#top forum 
top_forum <- fcheck %>% 
  count(forum) %>% 
  arrange(desc(n)) %>% 
  head(1) %>% 
  select(forum) %>% 
  pull() %>% 
  str_to_title()

#top forum - previous week only
top_prevweek_forum <- fcheck_PREVWEEK %>% 
  count(forum) %>% 
  arrange(desc(n)) %>% 
  head(1) %>% 
  select(forum) %>% 
  pull() %>% 
  str_to_title()



### count up individual subject categories  #### --------------------

tag_combined <- fcheck %>% 
  select(category_tags_combined) %>% 
  separate_rows(category_tags_combined, sep = ";") %>% 
  mutate(
    category_tags_combined = str_trim(category_tags_combined)
  )

#filter out NAs and blanks
tag_combined <- tag_combined %>% 
  filter(!is.na(category_tags_combined), category_tags_combined != "") 

category_tag_count <- tag_combined %>% 
  count(category_tags_combined) %>% 
  arrange(desc(n))


### Now the same for PREV WEEK ONLY
tag_combined_PREVWEEK <- fcheck_PREVWEEK %>% 
  select(category_tags_combined) %>% 
  separate_rows(category_tags_combined, sep = ";") %>% 
  mutate(
    category_tags_combined = str_trim(category_tags_combined)
  )

#filter out NAs
tag_combined_PREVWEEK <- tag_combined_PREVWEEK %>% 
  filter(!is.na(category_tags_combined), category_tags_combined != "") 

category_tag_PREVWEEK_count <- tag_combined_PREVWEEK %>% 
  count(category_tags_combined) %>% 
  arrange(desc(n))


#subject count - all
subject_count <- category_tag_count %>% 
  nrow()

#subject count - previous week only
subject_count_PREVWEEK <- category_tag_PREVWEEK_count %>% 
  nrow()



### count up coce_name variations #### --------------------

#top kind of code name - previous week only
top_prevweek_code_name <- fcheck_PREVWEEK %>% 
  filter(code_name != "") %>% 
  count(code_name) %>% 
  arrange(desc(n)) %>% 
  head(1) %>% 
  select(code_name) %>% 
  pull() %>% 
  str_to_title()

#number of code names from previous week
count_prevweek_code_name <- fcheck_PREVWEEK %>% 
  filter(code_name != "") %>% 
  count(code_name) %>% 
  nrow()

#number of all code names 
count_code_name <- fcheck %>% 
  filter(code_name != "") %>% 
  count(code_name) %>% 
  nrow()


#save copy in case needed
write_xlsx(fcheck, "saved_versions/fcheck_temp.xlsx")
saveRDS(fcheck, "saved_versions/fcheck_temp.rds")

# 
# zzz <- fcheck %>% 
#   count(code_name, category_tags_combined)
# 
# write_xlsx(zzz, "saved_versions/codelisttoclean.xlsx")


#an unique id to fcheck
# fcheck <- rowid_to_column(fcheck, "recno")


# set time object set to eastern time
d <- Sys.Date()
# d <- .POSIXct(d, "EST")
  
t <- Sys.time()
# t <- .POSIXct(t, "EST")

```


Searchable Database 
===================================== 
Trump false claims compiled by CNN. To **filter** the list, click on the boxes above the columns. To **sort**, click on the arrows by the column names. To **search globally** by keywords, use the search box on the right. 
(Last updated on `r format(t, format="%B %d %I:%M %p %Z")`)


Row 
-----------------------------------------------------------------------

### {data-width=800}

```{r searchable_table}

#searchable table

fcheck_table <- fcheck %>% 
  select(date,
         kind_of_forum,
         forum,
         location,
         state,
         claim,
         fact_check,
         category_tags_combined,
         code_name,
         source_article
) %>% 
  arrange(desc(date))

datatable(fcheck_table, 
          rownames = FALSE, 
          filter = "top",
          escape = FALSE,
          options = list(searchHighlight = TRUE)) %>% 
  formatDate('date', 'toDateString') %>% 
  formatStyle('claim', fontStyle = 'italic')


```



Summary Counts (Most Recent Week) 
===================================== 
Aggregate counts of all Trump false claims made over the **`r week_range_string`**. 


Row {data-height=200}
-----------------------------------------------------------------------

### Number of false claims for the week

```{r }

tot <- count_prevweek_total

valueBox(tot, icon = "fa-pencil", color = "blue")


```

### Number of forums for the week

```{r}

num_forums <- count_prevweek_forum %>% 
  filter(!is.na(forum)) %>% 
  nrow()

valueBox(num_forums, icon = "fa-users", color = "green")


```

### Number of subjects for the week 

```{r}

valueBox(subject_count_PREVWEEK, icon = "fa-book", color = "darkred")



```


### Number of code names for the week 

```{r}

valueBox(count_prevweek_code_name, icon = "fa-book", color = "purple")



```



Row {data-height=800}
-----------------------------------------------------------------------


### Daily totals this week

```{r}

bydate <- fcheck_PREVWEEK %>%
  count(date) %>% 
  ungroup() 


d <- ggplot(data = bydate, aes(x = date, y = n)) +
  geom_col(
    # color = "#848484",
    fill = "lightblue") +
  # coord_flip() +
  theme_minimal()

d2 <- d + labs(x ="", y = "") +
  theme(plot.title = element_text(hjust = 0.5)) +
  # scale_fill_manual(values=cbPalette) +
  theme(legend.title=element_blank()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

dd <- ggplotly(d2)

dd_nomenu <- dd %>% config(displayModeBar = FALSE)
dd_nomenu

# ggplot(corr.m, aes(x = reorder(miRNA, -value), y = value, fill = variable)) +
#   geom_bar(stat = "identity")

```


### Top forums

```{r}

byforum <- fcheck_PREVWEEK %>%
  filter(!is.na(forum)) %>% 
  count(forum) %>%
  arrange(desc(n)) %>%
  head() %>%
  ungroup()


e <- ggplot(data = byforum, aes(x = reorder(forum, -n), y = n)) +
  geom_col(
    # color = "#848484",
    fill = "#A8E9A8") +
  # coord_flip() +
  theme_minimal()

e2 <- e + labs(x ="", y = "") +
  theme(plot.title = element_text(hjust = 0.5)) +
  # scale_fill_manual(values=cbPalette) +
  theme(legend.title=element_blank()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ee <- ggplotly(e2)

ee_nomenu <- ee %>% config(displayModeBar = FALSE)
ee_nomenu


```


### Top subjects

```{r}

bysubject <- category_tag_PREVWEEK_count %>% 
  filter(category_tags_combined != "") %>% 
  head()


e <- ggplot(data = bysubject, aes(x = reorder(category_tags_combined, -n), y = n)) +
  geom_col(
    # color = "#848484",
    fill = "#f4a8a7") +
  # coord_flip() +
  theme_minimal()

e2 <- e + labs(x ="", y = "") +
  theme(plot.title = element_text(hjust = 0.5)) +
  # scale_fill_manual(values=cbPalette) +
  theme(legend.title=element_blank()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ee <- ggplotly(e2)

ee_nomenu <- ee %>% config(displayModeBar = FALSE)
ee_nomenu


```


### Top code names

```{r}

bycodename <- fcheck_PREVWEEK %>% 
  filter(code_name != "") %>% 
  count(code_name) %>% 
  ungroup() %>% 
  head()



g <- ggplot(data = bycodename, aes(x = reorder(code_name, -n), y = n)) +
  geom_col(
    # color = "#848484",
    fill = "#DA85E8") +
  # coord_flip() +
  theme_minimal()

g2 <- g + labs(x ="", y = "") +
  theme(plot.title = element_text(hjust = 0.5)) +
  # scale_fill_manual(values=cbPalette) +
  theme(legend.title=element_blank()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = function(x) unique(floor(pretty(seq(0, (max(x) + 1) * 1.1)))))

gg <- ggplotly(g2)

gg_nomenu <- gg %>% config(displayModeBar = FALSE)
gg_nomenu


```





Summary Counts (All) 
===================================== 
Aggregate counts of *all* Trump false claims compiled by CNN **since `r format(min(fcheck$date), "%a %b %d")`**


Row {data-height=200}
-----------------------------------------------------------------------

### Number of all false claims 

```{r count_total_box}

tot <- count_total

valueBox(tot, icon = "fa-pencil", color = "blue")


```

### Number of all forum types

```{r}

num_forums <- count_forum_kind %>% 
  nrow()

valueBox(num_forums, icon = "fa-users", color = "green")


```

### Number of all subjects 

```{r}

valueBox(subject_count, icon = "fa-book", color = "darkred")



```


### Number of all code names 

```{r}

valueBox(count_code_name, icon = "fa-book", color = "purple")



```




Row {data-height=800}
-----------------------------------------------------------------------


### Top daily totals

```{r}

bydate <- fcheck %>%
  count(date) %>% 
  arrange(desc(n)) %>%
  head() %>% 
  ungroup() 


d <- ggplot(data = bydate, aes(x = reorder(date, -n), y = n)) +
  geom_col(
    # color = "#848484",
    fill = "lightblue") +
  # coord_flip() +
  theme_minimal()

d2 <- d + labs(x ="", y = "") +
  theme(plot.title = element_text(hjust = 0.5)) +
  # scale_fill_manual(values=cbPalette) +
  theme(legend.title=element_blank()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

dd <- ggplotly(d2)

dd_nomenu <- dd %>% config(displayModeBar = FALSE)
dd_nomenu

# ggplot(corr.m, aes(x = reorder(miRNA, -value), y = value, fill = variable)) +
#   geom_bar(stat = "identity")

```


### Top forum types

```{r}

byforumtype <- fcheck %>%
  count(kind_of_forum) %>%
  arrange(desc(n)) %>%
  head() %>%
  ungroup()

e <- ggplot(data = byforumtype, aes(x = reorder(kind_of_forum, -n), y = n)) +
  geom_col(
    # color = "#848484",
    fill = "#A8E9A8") +
  # coord_flip() +
  theme_minimal()

e2 <- e + labs(x ="", y = "") +
  theme(plot.title = element_text(hjust = 0.5)) +
  # scale_fill_manual(values=cbPalette) +
  theme(legend.title=element_blank()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ee <- ggplotly(e2)

ee_nomenu <- ee %>% config(displayModeBar = FALSE)
ee_nomenu


```


### Top subjects

```{r}

bysubject_all <- category_tag_count %>% 
  filter(category_tags_combined != "") %>% 
  head()


e <- ggplot(data = bysubject_all, aes(x = reorder(category_tags_combined, -n), y = n)) +
  geom_col(
    # color = "#848484",
    fill = "#f4a8a7") +
  # coord_flip() +
  theme_minimal()

e2 <- e + labs(x ="", y = "") +
  theme(plot.title = element_text(hjust = 0.5)) +
  # scale_fill_manual(values=cbPalette) +
  theme(legend.title=element_blank()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ee <- ggplotly(e2)

ee_nomenu <- ee %>% config(displayModeBar = FALSE)
ee_nomenu


```


### Top code names

```{r}

bycodename <- fcheck %>% 
  filter(code_name != "") %>% 
  count(code_name) %>% 
  ungroup() %>% 
  head()



g <- ggplot(data = bycodename, aes(x = reorder(code_name, -n), y = n)) +
  geom_col(
    # color = "#848484",
    fill = "#DA85E8") +
  # coord_flip() +
  theme_minimal()

g2 <- g + labs(x ="", y = "") +
  theme(plot.title = element_text(hjust = 0.5)) +
  # scale_fill_manual(values=cbPalette) +
  theme(legend.title=element_blank()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = function(x) unique(floor(pretty(seq(0, (max(x) + 1) * 1.1)))))

gg <- ggplotly(g2)

gg_nomenu <- gg %>% config(displayModeBar = FALSE)
gg_nomenu


```



Time-based Rankings
===================================== 



Row 
-----------------------------------------------------------------------

### Daily tallies for `r week_range_string`

```{r}

fcheck_PREVWEEK %>% 
  count(date) %>% 
  arrange(date) %>% 
  mutate(
    rank = min_rank(desc(n)),
    date = format(date, "%b %d")      
    ) %>% 
    kable() %>%
    kable_styling(bootstrap_options = c("striped"))


```


### Top individual days (all since `r format(min(fcheck$date), "%a %b %d")`)

```{r}

fcheck %>% 
  count(date) %>% 
  arrange(desc(n)) %>% 
  head(5) %>% 
  mutate(
    rank = min_rank(desc(n)),
    date = format(date, "%b %d")      
    ) %>% 
    kable() %>%
    kable_styling(bootstrap_options = c("striped"))


```


### Top weeks 

```{r}

fcheck %>% 
  count(year, isoweek) %>% 
  arrange(desc(n)) %>% 
  head(5) %>% 
  mutate(rank = min_rank(desc(n))) %>% 
  rename(week = isoweek) %>% 
    kable() %>%
    kable_styling(bootstrap_options = c("striped"))



```


### Top months 

```{r}

fcheck %>% 
  count(year, month) %>% 
  arrange(desc(n)) %>% 
  head(5) %>% 
  mutate(rank = min_rank(desc(n))) %>% 
    kable() %>%
    kable_styling(bootstrap_options = c("striped"))


```


Row {data-height=200}
-----------------------------------------------------------------------


### Average claims per day during `r week_range_string`

```{r}

sumforprevweek <- fcheck_PREVWEEK %>% 
  count(date) %>% 
  summarise(sum(n)) %>% 
  pull() 

avg_per_day_prevweek <- round_half_up(sumforprevweek / 7, digits = 1)

valueBox(avg_per_day_prevweek, color = "#9c9293")


```


### Average claims per day since `r format(min(fcheck$date), "%a %b %d")`

```{r}

# https://data.library.virginia.edu/working-with-dates-and-time-in-r-using-the-lubridate-package/
# calculate total number of days since first recorded date
start <- min(fcheck$date)
end <- today()
#calculate elapsed time interval
elapsed.time <- start %--% end
#calculate duration of days
totaldays_sincestart <- as.duration(elapsed.time) / ddays(1)

#now we'll sum up the total of false claims per day
sumdailytotals <- fcheck %>% 
  count(date) %>% #might not need this step at all anymore
  summarise(sum(n)) %>% 
  pull() 

#calculate average
avg_per_day_all <- round_half_up(sumdailytotals / totaldays_sincestart, digits = 1)

valueBox(avg_per_day_all, color = "#9c9293")


```



### Average claims per week

```{r}

avg_per_week <- fcheck %>% 
  count(isoweek) %>% 
  summarise(mean(n)) %>% 
  pull()%>% 
  round_half_up(digits = 1)

valueBox(avg_per_week, color = "#9c9293")

```


### Average claims per month

```{r}

avg_per_month <- fcheck %>% 
  count(month) %>% 
  summarise(mean(n)) %>% 
  pull() %>% 
  round_half_up(digits = 1)

valueBox(avg_per_month, color = "#9c9293")

```


Row 
-----------------------------------------------------------------------

### Timeline of daily false claims

```{r}

bydate <- fcheck %>%
  count(date) 


p <- plot_ly(bydate, x = ~date, y = ~n, name = 'claimsperday', type = 'scatter',
             mode = 'lines+markers', connectgaps = TRUE)

p %>% config(displayModeBar = FALSE)





```

### TBD




Forum-based Rankings
===================================== 



Row 
-----------------------------------------------------------------------

### REMARKS with the most false claims

```{r}

fcheck %>% 
  count(kind_of_forum, date, forum) %>% 
  filter(kind_of_forum == "REMARKS") %>% 
  mutate(
    date = format(date, "%b %d")      
    ) %>%
  arrange(kind_of_forum, desc(n)) %>% 
  head(5) %>% 
    kable() %>%
    kable_styling(bootstrap_options = c("striped", "condensed"))


```


<!-- ### INFORMAL REMARKS with the most false claims -->

<!-- ```{r} -->

<!-- fcheck %>%  -->
<!--   count(kind_of_forum, date, forum) %>%  -->
<!--   filter(kind_of_forum == "INFORMAL REMARKS") %>%  -->
<!--   mutate( -->
<!--     date = format(date, "%b %d")       -->
<!--     ) %>% -->
<!--   arrange(kind_of_forum, desc(n)) %>%  -->
<!--   head(5) %>%  -->
<!--     kable() %>% -->
<!--     kable_styling(bootstrap_options = c("striped", "condensed")) -->


<!-- ``` -->


### SPEECHES with the most false claims

```{r}

fcheck %>% 
  count(kind_of_forum, date, forum) %>% 
  filter(kind_of_forum == "SPEECH") %>% 
  mutate(
    date = format(date, "%b %d")      
    ) %>%
  arrange(kind_of_forum, desc(n)) %>% 
  head(5) %>% 
    kable() %>%
    kable_styling(bootstrap_options = c("striped", "condensed"))


```


<!-- ### RALLY SPEECHES with the most false claims -->

<!-- ```{r} -->

<!-- fcheck %>%  -->
<!--   count(kind_of_forum, date, forum) %>%  -->
<!--   filter(kind_of_forum == "RALLY SPEECH") %>%  -->
<!--   mutate( -->
<!--     date = format(date, "%b %d")       -->
<!--     ) %>% -->
<!--   arrange(kind_of_forum, desc(n)) %>%  -->
<!--   head(5) %>%  -->
<!--     kable() %>% -->
<!--     kable_styling(bootstrap_options = c("striped", "condensed")) -->


<!-- ``` -->


### EXCHANGES WITH REPORTERS with the most false claims

```{r}

fcheck %>% 
  count(kind_of_forum, date, forum) %>% 
  filter(kind_of_forum == "EXCHANGE WITH REPORTERS") %>% 
  mutate(
    date = format(date, "%b %d")      
    ) %>%
  arrange(kind_of_forum, desc(n)) %>% 
  head(5) %>% 
    kable() %>%
    kable_styling(bootstrap_options = c("striped", "condensed"))


```


Row
-----------------------------------------------------------------------

### INTERVIEWS with the most false claims

```{r}

fcheck %>% 
  count(kind_of_forum, date, forum) %>% 
  filter(kind_of_forum == "INTERVIEW") %>% 
  mutate(
    date = format(date, "%b %d")      
    ) %>%
  arrange(kind_of_forum, desc(n)) %>% 
  head(5) %>% 
    kable() %>%
    kable_styling(bootstrap_options = c("striped", "condensed"))


```



### TWEETS with the most false claims

```{r}

fcheck %>% 
  count(kind_of_forum, date, forum) %>% 
  filter(kind_of_forum == "TWEET") %>% 
  mutate(
    date = format(date, "%b %d")      
    ) %>%
  arrange(kind_of_forum, desc(n)) %>% 
  head(5) %>% 
    kable() %>%
    kable_styling(bootstrap_options = c("striped", "condensed"))


```


<!-- ### EVENTS with the most false claims -->

<!-- ```{r} -->

<!-- fcheck %>%  -->
<!--   count(kind_of_forum, date, forum) %>%  -->
<!--   filter(kind_of_forum == "EVENT") %>%  -->
<!--   mutate( -->
<!--     date = format(date, "%b %d")       -->
<!--     ) %>% -->
<!--   arrange(kind_of_forum, desc(n)) %>%  -->
<!--   head(5) %>%  -->
<!--     kable() %>% -->
<!--     kable_styling(bootstrap_options = c("striped", "condensed")) -->


<!-- ``` -->


